Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-13 chapters/LBM_technique.tex
Changes 1. Added correct copyright statements to reused images 2. Cleaned up text in introduction, lit review and methods sections

\begin{figure}[h]
    \centering
    \includegraphics[scale = 1]{figures/methods/d3q19_lattice.jpg}
    \caption{D3Q19 lattice demonstrating the rest, nearest and next nearest direction that correspond to the 19 
    directions $(i)$ of the lattice with lattice velocity $c_{i}$. \cite{schmieschek_lb3d_2017} Reproduced from 
    Schmieschek et al. Computer Physics Communications 2017, 217, 149--161, under the CC-BY license.}
    \label{fig:d3q19_lattice}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[scale = 1]{figures/methods/d3q19_lattice.jpg}
    \caption{D3Q19 lattice demonstrating the rest, nearest and next nearest direction that correspond to the 19 
    directions $(i)$ of the lattice with lattice velocity $c_{i}$. Reprint of Figure 1 from
    \textit{Schmieschek, S.; Shamardin, L.; Frijters, S.; Krüger, T.; Schiller, U. D.; Harting, J.; Coveney, P. V. LB3D: A Parallel Implementation of the Lattice-Boltzmann Method for Simulation of Interacting Amphiphilic Fluids. Computer Physics Communications 2017, 217, 149-161} 
    with permission from Elsevier under the CC-BY license.}
    \label{fig:d3q19_lattice}
\end{figure}

### 2025-04-13 chapters/introduction_new.tex
Changes 1. Added correct copyright statements to reused images 2. Cleaned up text in introduction, lit review and methods sections

Compared to surfactant-stabilized emulsions, particle-stabilized emulsions (Pickering emulsions) exhibit enhanced resistance to coalescence and coarsening
due to the irreversibility of particle adsorption at the interface \cite{ngai_particle-stabilized_2015} .
Additionally, growing environmental and toxicity concerns associated with small-molecule surfactants have increased interest in the applications of particle-stabilized emulsions.
\cite{kaczerewska_environmental_2020, lechuga_acute_2016}. In contrast, particle stabilizers lower toxicity and improved biocompatibility, in addition to 
sustainable sourcing from particles based on cellulose or chitin. \cite{fujisawa_nanocellulose-stabilized_2017, tang_stimuli-responsive_2016, kalliola_carboxymethyl_2018}.
The microstructure of Pickering emulsions has been extensively studied, notably by Binks and Lumsdon in the early 2000s. Their investigations revealed that the emulsion droplet radius 
follows the relationship $R_e \propto \frac{\phi_w}{\phi_p}$, where $\phi_w$ and $\phi_p$ represent the volume fractions of water and particles, respectively \cite{binks_pickering_2001}. 
They also identified key parameters influencing microstructure, such as fluid composition and particle wettability. Neutrally wetting particles tend to stabilize nearly spherical droplets, 
while non-neutrally wetting particles can induce curvature, leading to the formation of bridged droplets, capillary aggregates, and other anisotropic structures, as illustrated in 
Figure~\ref{fig:state_diagram_particle_emulsions}.

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{figures/literature_review/state_diagram.jpg}
    \caption{Formation criteria for a particle stabilized emulsion that can form bijel \cite{velankar_non-equilibrium_2015}.
            Used with permission of Royal Society of Chemistry, from A non-equilibrium state diagram for liquid/fluid/particle 
            mixtures, Velankar, 1, 11, 2015 under license number 1551968-1}
    \label{fig:state_diagram_particle_emulsions}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{figures/introduction/bijel_coarsening.jpg}
    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the 
    interfacial area matches the cross sectional area of the adsorbed particles\cite{stratford_colloidal_2005}. 
    Reproduced from K. Stratford et al., Science 309, 2198-2201(2005) under license number 5966820525314.}
    \label{fig:bijel_coarsen}
\end{figure}

Bijel microstructures are of interest because their bicontinuous, interpenetrating networks enable tunable transport and separation properties. The computational discovery of the technique to 
synthesize bijels was succeeded by the experimental synthesis of a bijel in 2007 by Herzig et al., who used a 2,6-lutidine/water system stabilized with surface-modified silica particles
\cite{herzig_bicontinuous_2007}.
This binary fluid system exhibits a lower critical solution temperature (LCST) of 34.1\textdegree C and a critical composition at approximately 28\% lutidine by weight. By preparing the mixture at this 
critical composition and heating it past the LCST, phase separation was thermally induced, a process known as Thermally Induced Phase Separation (TIPS). The system underwent coarsening until gelation 
occurred, forming a bijel. Since this initial experimental synthesis, TIPS has been widely used in laboratory-scale studies to synthesize a variety of small molecule, oligomeric, and polymeric systems 
\cite{tavacoli_novel_2011, lee_bicontinuous_2010, bai_dynamics_2015, ching_rapid_2021}.

However, industrial applications require continuous, scalable fabrication techniques capable of generating application specific tailored microstructures. STrIPS has emerged as a promising solution 
for this need. As illustrated in Figure~\ref{fig:strips}, STrIPS involves a ternary fluid system composed of two immiscible fluids 
and a solvent. In the initial stage (Figure~\ref{fig:strips}a), a casting mixture is prepared. Phase separation is then triggered by flowing a co-solvent past the mixture to extract the solvent 
(Figure~\ref{fig:strips}b). This solvent transfer must occur within the spinodal region of the ternary phase diagram to ensure spinodal decomposition. By adjusting flow rates of both the casting 
mixture and the solvent removal stream, the resulting bijel morphology can be finely controlled. STrIPS has been successfully employed in applications ranging from battery electrode templating to drug 
delivery systems, liquid-in-liquid printing, and the creation of intrinsically polymerizable bijels for freestanding structures 
\cite{garcia_scalable_2019, thorson_bijel-templated_2019, amirfattahi_fabrication_2024, ching_rapid_2021}. The method is flexible with respect to fluid choice, with 
the only requirement being a well-characterized phase diagram that keeps the system within the spinodal regime throughout the solvent exchange process. Other techniques based on
induced phase separation such as Vapor Induced Phase Separation(VIPS) and controlled coalescence of droplets to form bijels through shear (homogenization) have also been identified as techniques
to synthesize bijels \cite{wang_scalable_2020, huang_bicontinuous_2017}.

\begin{figure}
    \centering
    \includegraphics[scale = 5]{figures/introduction/STrIPS.jpg}
    \caption{Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
             the casting mixture through diffusion, demonstrating the working principal of STrIPS. \cite{haase_continuous_2015}. Reproduced with permission from Wiley-VCH Verlag GmbH 
             \& Co. KGaA from \textit{Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by 
             Solvent Transfer-Induced Phase Separation (STRIPS)}, Haase, M. F., Stebe, K. J., 
             \& Lee, D., \textit{Advanced Materials}, 27(44), 7065-7071, 2015 under license number 5913140219015}
    \label{fig:strips}
\end{figure}

@@

Despite these advances, a persistent limitation is that bijel microstructure remains tightly coupled to the composition of the casting mixture and the kinetics of phase separation. Achieving controlled 
morphology often requires fine-tuning of fluid concentrations or external conditions, which may not be feasible for all applications \cite{haase_continuous_2015, reeves_particle-size_2015}.
The ability to tune these structural features would significantly expand the versatility and functionality of bijel-based systems.
In many of the proposed applications such as water filtration membranes or drug delivery 
platforms, the morphology of the material plays a critical role in determining key functional properties, including back pressure, species selectivity, and transport dynamics
\cite{vanoli_bijels_2022, thorson_bijel-templated_2019, khan_nanostructured_2022}.

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/literature_review/interfacial_curvature.png}
    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations 
             around the particle \cite{loudet_capillary_2005}. Reprinted Figure 4 with permission from
             Loudet et al, Phys. Rev. Letter., 94, 08301, 2003 Copyright 2025 by the American Physical Society under license number RNP/25/FEB/088185}
    \label{fig:anisotropic_particle_interface}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 1.5]{figures/introduction/magnetophoresis_emulsion.jpeg}
    \caption{Enhanced oil recovery of oil from water using magnetically responsive emulsion stabilizers, allowing for 
             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields \cite{tham_magnetophoresis_2021}. 
             K. Tham, W. M. Ng, S. S. Leong, S. P. Yeap, S. C. Low, H. L. Lee and J. Lim. Magnetophoresis of magnetic pickering 
             emulsions under low field gradient: Macroscopic and microscopic motion. 37, 1811: Reprinted (adapted) with permission from 
             Langmuir 2021, 37, 5, 1811-1822. Copyright 2025 American Chemical Society.}
    \label{fig:magnetophoresis_droplet}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.4]{figures/introduction/anisotropic_particles_assembly.jpg}
    \caption{Assembly of prolate particles on a flat interface at various interfacial coverages and field strengths,
             showing the self assembly into chains that ellipsoidal particles can undergo under applied magnetic fields at
             interfaces. \cite{davies_assembling_2014} Reproduced from Davies et al. Adv. Mater., 26: 6715-6719 under the 
             Creative Commons CC BY license.}
    \label{fig:anisotropic_assembly}
\end{figure}

>>>>

Compared to surfactant-stabilized emulsions, particle-stabilized emulsions (Pickering emulsions) exhibit enhanced resistance to coalescence and coarsening
due to the irreversibility of particle adsorption at the interface \cite{ngai_particle-stabilized_2015} .
Additionally, growing environmental and toxicity concerns surrounding small-molecule surfactants have increased interest in particle-stabilized emulsions, due to their lower toxicity, 
enhanced biocompatibility, and potential for sustainable sourcing from renewable materials such as chitin and cellulose.
\cite{kaczerewska_environmental_2020, lechuga_acute_2016, fujisawa_nanocellulose-stabilized_2017, tang_stimuli-responsive_2016, kalliola_carboxymethyl_2018}.
The microstructure of Pickering emulsions has been extensively studied, notably by Binks and Lumsdon in the early 2000s. Their investigations revealed that the emulsion droplet radius 
follows the relationship $R_e \propto \frac{1}{\phi_p}$, where $\phi_p$ represent the volume fractions of particles \cite{binks_pickering_2001}. 
They also identified key parameters influencing microstructure, such as fluid composition and particle wettability. Neutrally wetting particles tend to stabilize nearly spherical droplets, 
while non-neutrally wetting particles can induce curvature, leading to the formation of bridged droplets, capillary aggregates, and other anisotropic structures, as illustrated in 
Figure~\ref{fig:state_diagram_particle_emulsions}.

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{figures/literature_review/state_diagram.jpg}
    \caption{Formation criteria for a particle stabilized emulsion that can form bijel. Reprinted Figure 3 with permission from the Royal Society of Chemistry from 
             \textit{Velankar, S. S. A Non-Equilibrium State Diagram for Liquid/Fluid/Particle Mixtures. Soft Matter 2015, 11 (43), 8393-8403}
             with permission from the Royal Society of Chemistry under license number 1551968-1; Permission conveyed through Copyright Clearence Center}
    \label{fig:state_diagram_particle_emulsions}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{figures/introduction/bijel_coarsening.jpg}
    \caption{Initiation and arrest of spinodal decomposition as particles adsorb onto the interface, followed by jamming once the 
            interfacial area matches the cross sectional area of the adsorbed particles. Reprint of Figure 1 from
            \textit{Stratford, K.; Adhikari, R.; Pagonabarraga, I.; Desplat, J.-C.; Cates, M. E. Colloidal Jamming at Interfaces: A Route to Fluid-Bicontinuous Gels. Science 2005, 309 (5744), 2198-2201}
            Reprinted with permission from AAAS under license number 5966820525314.}
    \label{fig:bijel_coarsen}
\end{figure}

Bijel microstructures are of interest because their bicontinuous, interpenetrating networks enable tunable transport and separation properties. The computational discovery of the technique to 
synthesize bijels was succeeded by the experimental synthesis of a bijel in 2007 by Herzig et al., who used a 2,6-lutidine/water system stabilized with surface-modified silica particles
\cite{herzig_bicontinuous_2007}.
This binary fluid system exhibits a lower critical solution temperature (LCST) of 34.1\textdegree C and a critical composition at approximately 28\% lutidine by weight. By preparing the mixture at this 
critical composition and heating it past the LCST, phase separation was induced in a process known as Thermally Induced Phase Separation (TIPS). The system underwent coarsening until particle
interactions at the interface jammed the microstructure in place, once the cross-sectional area of the particles matched the interfacial area, forming a bijel. Since this initial 
experimental synthesis, TIPS has been widely used in laboratory-scale studies to synthesize a variety of small molecule, oligomeric, and polymeric systems 
\cite{tavacoli_novel_2011, lee_bicontinuous_2010, bai_dynamics_2015, ching_rapid_2021}.

However, industrial applications require continuous, scalable fabrication techniques capable of generating application specific tailored microstructures. The thermal induction of phase separation
does not permit easy scale up due to limitations of suitable systems that forms bijels and the need to have constant cooling rates to ensure consistent microstructures through the entire reaction
vessel. Solvent Transfer Induced Phase Separation (STrIPS) has emerged as a promising solution to address these issues.
As illustrated in Figure~\ref{fig:strips}, STrIPS involves a ternary fluid system composed of two immiscible fluids 
and a solvent. In the initial stage (Figure~\ref{fig:strips}a), a casting mixture is prepared. Phase separation is then triggered by flowing a co-solvent past the mixture to extract the solvent 
(Figure~\ref{fig:strips}b). This solvent transfer must occur within the spinodal region of the ternary phase diagram to ensure spinodal decomposition. By adjusting flow rates of both the casting 
mixture and the solvent removal stream, the resulting bijel morphology can be finely controlled. STrIPS has been successfully employed in applications ranging from battery electrode templating to drug 
delivery systems, liquid-in-liquid printing, and the creation of intrinsically polymerizable bijels for freestanding structures 
\cite{garcia_scalable_2019, thorson_bijel-templated_2019, amirfattahi_fabrication_2024, ching_rapid_2021}. The method is flexible with respect to fluid choice, with 
the only requirement being a well-characterized phase diagram that keeps the system within the spinodal regime throughout the solvent exchange process. Other techniques based on
induced phase separation such as Vapor Induced Phase Separation(VIPS) and controlled coalescence of droplets to form bijels through shear (homogenization) have also been identified as techniques
to synthesize bijels \cite{wang_scalable_2020, huang_bicontinuous_2017, cai_bijels_2017}.

\begin{figure}
    \centering
    \includegraphics[scale = 5]{figures/introduction/STrIPS.jpg}
    \caption{Extrusion of the bijel casting mixture into a non-solvent bath, followed by removal of solvent from 
             the casting mixture through diffusion, demonstrating the working principal of STrIPS. \cite{haase_continuous_2015}. 
             Reprint of Figure 2 from 
             \textit{Haase, M. F.; Stebe, K. J.; Lee, D. Continuous Fabrication of Hierarchical and Asymmetric Bijel Microparticles, Fibers, and Membranes by Solvent Transfer-Induced Phase Separation (STRIPS). Advanced Materials 2015, 27 (44), 7065-7071}
             with permission from Wiley-VCH Verlag GmbH \& Co. KGaA under license number 5913140219015}
    \label{fig:strips}
\end{figure}

@@

Despite these advances, a limitation is that bijel microstructure remains tightly coupled to the composition of the casting mixture and the kinetics of phase separation. Achieving controlled 
morphology often requires fine-tuning of fluid concentrations or external conditions, which may not be feasible for all applications \cite{haase_continuous_2015, reeves_particle-size_2015}.
The ability to tune these structural features would significantly expand the versatility and functionality of bijel-based systems.
In many of the proposed applications such as water filtration membranes or drug delivery 
platforms, the morphology of the material plays a critical role in determining key functional properties, including back pressure, species selectivity, and transport dynamics
\cite{vanoli_bijels_2022, thorson_bijel-templated_2019, khan_nanostructured_2022}.

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{figures/literature_review/interfacial_curvature.png}
    \caption{Quadropolar capillary interactions around prolate ellipsoidal particles caused by interfacial deformations 
             around the particle. Reprinted Figure 4 with permission from
             \textit{Loudet, J. C.; Alsayed, A. M.; Zhang, J.; Yodh, A. G. Capillary Interactions Between Anisotropic Colloidal Particles. Phys. Rev. Lett. 2005, 94 (1), 018301}
             Copyright 2025 by the American Physical Society.}
    \label{fig:anisotropic_particle_interface}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 1.5]{figures/introduction/magnetophoresis_emulsion.jpeg}
    \caption{Enhanced oil recovery of oil from water using magnetically responsive emulsion stabilizers, allowing for 
             locomotion and controlled coalescence of cargo from a matrix phase using magnetic fields. Reprint of the graphical abstract from
             \textit{Tham, F. K.; Ng, W. M.; Leong, S. S.; Yeap, S. P.; Low, S. C.; Lee, H. L.; Lim, J. Magnetophoresis of Magnetic Pickering Emulsions Under Low Field Gradient: Macroscopic and Microscopic Motion. Langmuir 2021, 37 (5), 1811-1822}
             Reprinted (adapted) with permission from Langmuir 2021, 37, 5, 1811-1822. Copyright 2025 American Chemical Society.}
    \label{fig:magnetophoresis_droplet}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.4]{figures/introduction/anisotropic_particles_assembly.jpg}
    \caption{Assembly of prolate particles on a flat interface at various interfacial coverages and field strengths,
             showing the self assembly into chains that ellipsoidal particles can undergo under applied magnetic fields at
             interfaces. Reprint of Figure 3 from
             \textit{Davies, G. B.; Krüger, T.; Coveney, P. V.; Harting, J.; Bresme, F. Assembling Ellipsoidal Particles at Fluid Interfaces Using Switchable Dipolar Capillary Interactions. Advanced Materials 2014, 26 (39), 6715-6719}
             with permission from Wiley-VCH Verlag GmbH \& Co. KGaA under the Creative Commons CC BY license.}
    \label{fig:anisotropic_assembly}
\end{figure}

### 2025-04-13 chapters/lit_review_new.tex
Changes 1. Added correct copyright statements to reused images 2. Cleaned up text in introduction, lit review and methods sections

\begin{figure}
    \centering
    \includegraphics[scale = 0.7]{../figures/literature_review/phase_diagram.png}
    \caption{Schematic of a phase diagram obtained from a free energy curve demonstrating key features of the free energy landscape that correspond
             to the phase diagram. Reprinted Figure 1 from
             Guillen-Chable, F.; Bayona, A.; Rodríguez-Zapata, L. C.; Castano, E. Phase Separation of Intrinsically Disordered 
             Nucleolar Proteins Relate to Localization and Function. IJMS 2021, 22 (23), 13095. with permission under the Creative Common CC BY license.}
    \label{fig:phase_diagram}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{../figures/literature_review/particle_at_interface.png }
    \caption{Particle schematic at an interface demonstrating the various quantities of interest. Reprinted Figure 2.1 from
             Particle-Stabilized Emulsions and Colloids: Formation and Applications; Ngai, T., Bon, S. A. F., Eds.; RSC soft matter series; 
             with permission Royal Society of Chemistry, RSC Publishing Cambridge, 2015 under license number 1597404-1}
    \label{fig:pieranski_model}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{../figures/literature_review/curvature_driven_assembly.jpeg}
    \caption{Self assembly of particles at points of large curvature gradients. Reproduced from Figure 5 in Cavallaro, M.; Botto, L.; 
             Lewandowski, E. P.; Wang, M.; Stebe, K. J. Curvature-Driven Capillary Migration and Assembly of Rod-like Particles. 
             Proc. Natl. Acad. Sci. U.S.A. 2011, 108 (52), 20923-20928 under the CC-BY license}
    \label{fig:curvature_gradient}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{../figures/literature_review/rods_bijels.png}
    \caption{Bijels stabilized by rod like particles, demonstrating 'flippers' at the interface, which are particles that flip out of the interface due to stress from adjacent particles. 
             Reproduced from Figure 3 in Hijnen, N.; Cai, D.; Clegg, P. S. Bijels Stabilized Using Rod-like Particles. Soft Matter 2015, 11 (22), 4351-4355 under the CC-BY license}
    \label{fig:rod_bijel_flippers}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{../figures/literature_review/shear_suspensions.jpeg}
    \caption{Schematic of suspensions under shear demonstrating shear banding and shear aggregates modifying the rheological properties of a suspension. 
             Reproduced from Figure 2 in Wagner, N. J.; Brady, J. F. Shear Thickening in Colloidal Dispersions. Physics Today 2009, 62 (10), 27-32 under the CC-BY license}
    \label{fig:suspension_shear}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 4]{../figures/literature_review/Flow-curves.png}
    \caption{Schematic of expected shear stress as a function of applied shear rate for various models of fluids on the left and a shear thinning material on the right, demonstrating
             the yield stress at low strain rate followed by shear thinning and the infinite shear rate plateau. Reproduced from Cooke, M. E.; Rosenzweig, D. H. The Rheology of Direct 
             and Suspended Extrusion Bioprinting. APL Bioengineering 2021, 5 (1), 011502 under the CC BY license.}
    \label{fig:shear_theory}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[scale = 0.7]{../figures/literature_review/phase_diagram.png}
    \caption{Schematic of a phase diagram obtained from a free energy curve demonstrating key features of the free energy landscape that correspond
             to the phase diagram. Reprint of Figure 1 from 
             \textit{Guillen-Chable, F.; Bayona, A.; Rodríguez-Zapata, L. C.; Castano, E. Phase Separation of Intrinsically Disordered 
             Nucleolar Proteins Relate to Localization and Function. IJMS 2021, 22 (23), 13095.}
             with permission from MDPI under the Creative Common CC BY license.}
    \label{fig:phase_diagram}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.5]{../figures/literature_review/particle_at_interface.png }
    \caption{Particle schematic at an interface demonstrating the various quantities of interest. Used with permission of the Royal Society of Chemistry from 
             Figure 2.1 in \textit{Particle-Stabilized Emulsions and Colloids: Formation and Applications; Ngai, T., Bon, S. A. F., Eds.; RSC soft matter series;};
             Permission conveyed through Copyright Clearence Center, Inc. under license number 1597404-1.}
    \label{fig:pieranski_model}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{../figures/literature_review/curvature_driven_assembly.jpeg}
    \caption{Self assembly of particles at points of large curvature gradients. Reprint of Figure 5 in 
             \textit{Cavallaro, M.; Botto, L.; Lewandowski, E. P.; Wang, M.; Stebe, K. J. Curvature-Driven Capillary Migration and Assembly of Rod-like Particles. Proc. Natl. Acad. Sci. U.S.A. 2011, 108 (52), 20923-20928} 
             with permission from The National Academy of Sciences under the CC-BY license}
    \label{fig:curvature_gradient}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{../figures/literature_review/rods_bijels.png}
    \caption{Bijels stabilized by rod like particles, demonstrating 'flippers' at the interface, which are particles that flip out of the interface due to stress from adjacent particles. 
             Reprint of Figure 3 in 
             \textit{Hijnen, N.; Cai, D.; Clegg, P. S. Bijels Stabilized Using Rod-like Particles. Soft Matter 2015, 11 (22), 4351-4355} 
             with permission from the Royal Society of Chemistry under the CC-BY license.}
    \label{fig:rod_bijel_flippers}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 0.3]{../figures/literature_review/shear_suspensions.jpeg}
    \caption{Schematic of suspensions under shear demonstrating shear banding and shear aggregates modifying the rheological properties of a suspension. 
             Reprint of Figure 2 in \textit{Wagner, N. J.; Brady, J. F. Shear Thickening in Colloidal Dispersions. Physics Today 2009, 62 (10), 27-32}
             with permission from the American Institute of Physics under the CC-BY license}
    \label{fig:suspension_shear}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale = 4]{../figures/literature_review/Flow-curves.png}
    \caption{Schematic of expected shear stress as a function of applied shear rate for various models of fluids on the left and a shear thinning material on the right, demonstrating
             the yield stress at low strain rate followed by shear thinning and the infinite shear rate plateau. Reprint of Figure 2 from
             \textit{Cooke, M. E.; Rosenzweig, D. H. The Rheology of Direct and Suspended Extrusion Bioprinting. APL Bioengineering 2021, 5 (1), 011502} 
             with permission from the American Institute of Physics under the CC BY license.}
    \label{fig:shear_theory}
\end{figure}
